### 2023-06-24 chapter_2/src/appendix.qmd

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brakcets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_intercept" = "Intercept"
    , "b_dem_vote_share" = "Democratic vote share (%)"
  )
)
```

>>>>

## A note about discrepancies between the main text and the pre-registered report

I posted a pre-registration of my hypotheses [on OSF.](https://osf.io/e9gk8/) The pre-registration allows me to offer transparency about what I expect to find before I analyze any data. This reduces the amount of post-hoc rationalization of any findings pulled from the data. The pre-registered hypotheses are the same as those that are tested here. Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing. In the spirit of complete transparancy, I wanted to make a note of these differences.

Again, the hypotheses that I pre-registered remain the same as what is presented in the main text. The research design also remained the same. During the IRB process, I had to make some decisions about space considerations as I was concerned about participants taking longer than the advertised time (6 minutes). Due to these concerns, I removed some questions. Namely, I no longer asked participants about the color of the yard sign after viewing it nor did I include a battery for political knowledge. These were changes that I made during the IRB process, but did not change in my pre-registered report. In full transparency, mostly because I forgot to make the update as well as having some issues with Dropbox at the time. Removing these questions also had principled reasons. First, I did not want to inflate the treatment effect by asking participants to reflect and tell me the color they saw and then report the partisanship of the candidate. I wanted to get as close to a snap-judgment as I could get and I wanted to immediately ask participants about the partisanship of the candidate after viewing the yard sign to accomplish this goal. For the political knowledge battery, I discuss why I elected to use attention over knowledge in the main text of the chapter. But further, the prevailing questions on political knowledge are suspect as they provide factual information that can be googled participants during the study. Given the length of time it would take for participants to respond to these additional questions and concerns about what value they provide, I did not include them. Those who would like to confirm, I have the IRB materials posted on [my github](https://github.com/DamonCharlesRoberts/color_as_political_information/tree/30508e8f4100c7e19382611fe046ed936c1fdb42/src/assets/irb) which you can see the history of these files.

Another set of discrepancies is some of my modeling strategies. As I note in the main text, some of the data from the mouseview exercise are not exactly what I had expected initially. I do not have much information about the size of the screen participants had nor do I have precise data for when participants were able to view the yard sign during those 5 seconds that it was up. The data for each trial began recording on an instruction screen that I used to standardize cursor starting position and when they finished the trial. As there is a lot of variation between when participants stopped viewing the instructions, I can't be sure which cursor movements were during the display of the yard sign. Because of the noisiness of the mouseview data, I simplified some of my analyses for $H_1$ and $H_4$.

For $H_5$, I had mentioned that I would include an analysis with a synthetic control. However, the district-level data available at the time of writing is not yet available. Because of this, I cannot leverage redistricting patterns for better causal identification of the question of whether campaigns respond to district characteristics or if they anticipate them. Therefore, I stick with the more descriptive task. Relatedly, I had indicated I would use a multilevel model by using intercepts that partially pool at the district level and intercepts that are not pooled at the state level. Upon further reflection on this strategy, this seemed inappropriate for the question at hand as I did not have clear expectations about variation within states but rather more generally was asking a question about districts at large. Further, I did not specify that I would be using a beta regression for these models so many may read my pre-registration as me implying that I would use ordinary least squares. This is totally reasonable. However, out of concern with reporting results that are extremely unstable because of poor choice in estimator as I discuss in the main text and later in the appendix, the ordered beta regression provides more stable results that I am comfortable making inferences with.

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  list_fitted_split_1
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_2
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_age" = "Age"
    , "b_trial_1_red_stimuli:age" = "Red yard sign $\\times$ Age"
    , "b_trial_1_blue_stimuli:age" = "Blue yard sign $\\times$ Age"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  list_fitted_split_3
  , coef_map = c(
    "b_trial_1_red_stimuli_alt" = "Red yard sign"
    , "b_trial_1_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brakcets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Redefine names
list_fitted_split_4 <- list(
  "Red - Color blindness moderating" = list_fitted[["h_2"]][["red_colorblind"]]
  , "Blue - Color blindness moderating" = list_fitted[["h_2"]][["blue_colorblind"]]
)
# Make table
modelsummary(
  list_fitted_split_4
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_trial_1_red_stimuli:color_blind_dummy" = "Red yard sign $\\times$ Color blind"
    , "b_trial_1_blue_stimuli:color_blind_dummy" = "Blue yard sign $\\times$ Color blind"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
  )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_2_red_stimuli" = "Red yard sign"
    , "b_trial_2_blue_stimuli" = "Blue yard sign"
    , "b_trial_2_red_stimuli_alt" = "Red yard sign"
    , "b_trial_2_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Change goodness of fit stuff
gm <- list(
  list("raw" = "nobs", "clean" = "Num.Obs.", "fmt" = 1)
  , list("raw" = "r.squared", "clean" = "$R^2$", "fmt" = 2)
  , list("raw" = "waic", "clean" = "WAIC", "fmt" = 2)
)
# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_3_red_stimuli" = "Red yard sign"
    , "b_trial_3_blue_stimuli" = "Blue yard sign"
    , "b_trial_3_red_stimuli_alt" = "Red yard sign"
    , "b_trial_3_blue_stimuli_alt" = "Blue yard sign"
    , "b_Intercept[1]" = "Intercept 1"
    , "b_Intercept[2]" = "Intercept 2"
    )
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

# Make table
modelsummary(
  model_names
  , coef_map = c(
    "b_trial_1_red_stimuli" = "Red yard sign"
    , "b_trial_1_blue_stimuli" = "Blue yard sign"
    , "b_pid_7" = "Party ID"
    , "b_trial_1_red_stimuli:pid_7" = "Red yard sign $\\times$ Party ID"
    , "b_trial_1_blue_stimuli:pid_7" = "Blue yard sign $\\times$ Party ID"
    , "b_attention" = "Attention"
    , "b_age" = "Age"
    , "b_gender_idMale" = "Gender - Male"
    , "b_gender_idNonMbinary" = "Gender - Non-binary"
    , "b_gender_idPrefernottochoose" = "Gender - Prefer not to choose"
    , "b_race_idBlacknonMhispanic" = "Black"
    , "b_race_idHispanice" = "Hispanic"
    , "b_race_idMultipleraces" = "Multiple races"
    , "b_race_idNativeAmericanDAlaskaNativeOrOtherRace" = "Other race"
    , "b_race_idWhitenonMhispanic" = "White"
  )  
  , statistic = "conf.int"
  , conf_level = 0.9
  , gof_map = gm 
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , " of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , " of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```

@@

names(list_fitted[["h_5"]]) <- c("Prop. yard sign Red", "Prop. yard sign Blue")
modelsummary(
  list_fitted[["h_5"]]
  , stat = "conf.int"
  , conf_level = 0.9
  , metrics = c("n.obs", "RMSE")
  , coef_map = c(
    "b_intercept" = "Intercept"
    , "b_dem_vote_share" = "Democratic vote share (%)"
  )
  , notes = c(
    "Data source: Pavlovia"
    , "Positive coefficients reflect the logged-odds"
    , "of claiming candidate is Republican."
    , "Numbers inside brackets reflect the 5th and 95th percentile"
    , "of the draws from the posterior distribution."
  )
  , escape = FALSE
  , output = "latex"
)
```
